DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Imported WDI data

@@

#### Import WDI Annual GDP Growth Data ####
WDIsearch('gdp')
dat = WDI(indicator='GDP growth (annual %)', country=c('MX','CA','US',), start=2001, end=2013)

>>>>

# Load citation package
pkgs <- c('repmis', 'tidyr', 'reshape2', 'plyr', 'WDI')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

@@

#### Import WDI Annual GDP Growth Data ####
WDIsearch('gdp')
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))

# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"

# Recode country == "Korea, Rep."" to "Korea (South)"
GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"

# Remove iso2c data to ease merge with FinalMerge data
GDPGrowth$iso2c <- NULL

# Merge GDPGrowth and FinalMerge
CompeteDataset <- merge(FinalMerge, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)
